Symbolic Abstract Data Type Inference

### 2015-07-07 draft.tex
Fixed space hacks.
Updated to POPL format.
Adding motivation section.
Updated the title with “Symbolic”.
starting top-down presentation
Abstract algorithm.
restructuring the technical part
Updated the abstract.

\documentclass[10pt,preprint,nocopyrightspace,natbib,authoryear]{sigplanconf}

\usepackage[utf8]{inputenc}
\usepackage{microtype}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{example}{Example}
\newtheorem{definition}{Definition}
\DeclareMathOperator{\dom}{dom}
\DeclareMathOperator{\img}{img}
\DeclareMathOperator{\width}{width}
\DeclareMathOperator{\weight}{weight}
\DeclareMathOperator{\freq}{freq}

@@

@@

\title{Abstract Data Type Inference}
% \subtitle{}

@@

  Formal specifications are a vital component to the automated verification of
  software systems. In the case of efficient implementations of concurrent
  objects like atomic registers, queues, and locks, checking adherence to their
  abstract data types (ADTs) is a difficult problem, yet can be made tractable
  when the ADT specifications are given by symbolic, logical representations.
  Obtaining these symbolic representations, however, is a complex task
  requiring rare expertise. In practice, concurrent objects are specified
  indirectly by imperative reference implementations.

@@

\input intro
\input histories
\input inference
\input patterns
\input formula
\input matching
\input nature
\input discussion
\input related

@@

>>>>

\documentclass[9pt,preprint,nocopyrightspace,natbib,authoryear]{sigplanconf}

\usepackage[utf8]{inputenc}
\usepackage{microtype}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{listings}

\lstset{
  basicstyle=\ttfamily,
  mathescape
}

\newtheorem{theorem}{Theorem}
\newtheorem{remark}{Remark}
\newtheorem{lemma}{Lemma}
\newtheorem{example}{Example}
\newtheorem{definition}{Definition}
\DeclareMathOperator{\dom}{dom}
\DeclareMathOperator{\img}{img}
\DeclareMathOperator{\width}{width}
\DeclareMathOperator{\weight}{weight}
\DeclareMathOperator{\freq}{freq}

@@

\makeatletter
\renewcommand{\verbatim@font}{\normalfont\ttfamily\scriptsize}
\makeatother

@@

\title{Symbolic Abstract Data Type Inference}
% \subtitle{}

@@

  Formal specifications are a vital component to the scalable verification of
  software systems. In the case of efficient implementations of concurrent
  objects like atomic registers, queues, and locks, symbolic representations
  of their abstract data types (ADTs) enable efficient modular reasoning,
  decoupling clients from implementations. Writing adequate formal
  specifications, however, is a complex task requiring rare expertise. In
  practice, concurrent objects are specified indirectly by reference
  implementations.

@@

\input intro
\input motivation
\input histories
\input inference
\input patterns
\input formula
\input algorithm
\input matching
\input nature
\input discussion
\input related

@@

\input appendix
